SciPy - some descriptive title here

### 2018-06-27 scipy-1.0/paper.tex

\subsection*{Data structures}
\textbf{cKDTree}
\textbf{Sparse matrices}

\subsection*{Unified bindings to compiled code}
LowLevelCallable

>>>>

\subsection*{Data structures}
\textbf{cKDTree}
\input{ckdtree}
\textbf{Sparse matrices}

\subsection*{Unified bindings to compiled code}
\subsubsection*{LowLevelCallable}
As of SciPy version 0.19, it is possible for users to wrap low-level
functions in a \texttt{scipy.LowLevelCallable()} object that reduces
the overhead for calling compiled C functions directly from Python.
Supported low-level functions include \texttt{PyCapsule} objects,
ctypes function pointers, and cffi function pointers. The low level
function signature must be consistent with the expectations of the
routine it is passed to. For example, the documentation for
\texttt{scipy.ndimage.generic\_filter} defines two acceptable C callback
function signatures that may be used to produce functions that operate
on each element of image data with low overhead. The C code may be
generated using numba or Cython, for example, as long as the function
call signature matches the specifications. Furthermore, it is even
possible to generate a low-level callback function automatically
from a Cython module using \texttt{scipy.LowLevelCallable.from\_cython}.
